%!TEX root = ../main.tex

This chapter will explain the background for this thesis, which is divided into sections. I start with the introduction of Visual Solutions and their practical problem. This section will also give a quick overview of how the application Virtual Arena works by describing its underlying architecture. Secondly, I will introduce the RTCWeb technologies and WebRTC browser APIs. Then I will look at the use of \gls{wrtc} on mobile devices. Finally, I will look at competing real-time communication vendors and similar work.

\section{Visual Solutions}
\input{chapters/virtualarena}

\newpage
\section{Introduction to WebRTC}
\input{chapters/wrtcintro}

\newpage
\section{Mobile devices}
\input{chapters/mobile-devices.tex}

\newpage
\section{Enterprise communication vendors}
\input{chapters/enterprise-communication-vendors.tex}

\newpage
\section{Similar work}
\input{chapters/similar-work.tex}

\newpage
\section{Background summary}
\gls{wrtc} provides the foundation to interoperate different systems more easily by standardizing real-time web communications. It is an effective tool that can be used to quickly create audio and video communication applications, with the added advantage of support for a variety of mobile devices. With the new APIs we can run a client on any tablet or mobile phone that has a web browser with support for the \gls{wrtc} standard. Related technologies developed by Cisco and Microsoft are more complete and are now dominating the communication space, but it's going to be interesting to see if they will lose some of their market share to smaller companies utilizing \gls{wrtc} in the near future. Some similar work has already been done, such as the webrtc2sip gateway created by Doubango Telecom.

Visual Solutions VA application is using transport technologies that need to have added security layers to work with \gls{wrtc}, and the media formats needs to be transcoded with the appropriate codecs. Also, signaling and routing needs to be enhanced to make VA work with \gls{wrtc}. In the next chapter I will describe the different problems that needs to be addressed.

%Google has successfully used \gls{wrtc} in their Hangout application and on their Chromecast devices. 