%!TEX root = ../main.tex

summarize your thesis again as in the introduction.
Describe how your evaluation revealed that your system is successful.
Describe future work in this area.

We have looked at some basic theory about streaming media in the web browser, and explained our experiments and their capabilities. In chapter x we looked at the testing data collected and did an analysis of the results. The results were discussed and conclusions were made. This chapter will summarize the key elements of the results, look at what contributions have been made, and suggest some future work.


To simulate a low latency environment all early experiments were done on a local network. After collecting data using different mechanisms of protocols and streaming media, they were compared with the results from the same experiments using a simulated external network. Data about traffic, latency, and cpu-load were gathered and analyzed. Then we discussed the results with regard to inconsistencies, trends, synergies between different factors, and potential conclusions that could be made.

Contributions to reseach

Future Work
Furter testing when different vendors have agreed on a common platform



%research on rtcweb


By researching on the integration of RTCWEB technology with enterpirse communication systems can helkp business utilize RTCWEB to provide services through INternet or mobile Internet using their existing infrastructure in combination with a gateway. The can extend their services by reaching a ton of new devices. 
Through the research, we describe an integration solution by adding an interworking gateway which include three subsystems- singaling gateway, media relay and address server. Suggested protocols include WebSockets and RTP.
Aside from theory, this solution can realize the integration of RTCWeb with an enterprise communication system but the realization need th supporting of by standardization work like protocol and codec defining. IETF's standardization work is progreseed very quickly. In the the future, we will focus on the progressing and refine the solution. At the same time, realize a prototype.